The first high-redshift Changing Look Quasars

### 2019-11-08 tex/other_tex/201911/CIV_CLQs_20191107.tex
other wee .tex updates

@@

In this paper we use the wavelengths of 1548.202 and 1550.774~\AA\ for
the \civ\ doublet \citep{Kramida2018}.  The 1548.202 and 1550.774 \AA\
emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$
transition, split by total angular momentum $J= 3/2$ and $1/2$,
resulting in energies 64,591 cm$^{-1}$ and 64,484 cm$^{-1}$,
respectively \citep[e.g.][]{Moore1993}. The transition probabilities
of the the 1548 and 1550\AA\ lines are $A_{ki}= 2.65\times10^{8}$ and
2.64$\times10^{8}$ s$^{-1}$.

The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$. Using the
\href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST
Atomic Spectra Database Ionization Energies Form} for ionisation
energies, we note 11.3 eV is the energy required for C~I to dislodge
one electron and become singly-ionised C~II; 24.4 eV is then the
(`additional') energy needed for singly-ionised C~II to dislodge an
additional electron, and become doubly-ionised C~III, and 47.89 eV
(3.519 Ry) is required for doubly-ionised C~III become triply-ionised
\civ.  64.49 eV (4.74 Ry) is the energy needed to ionize \civ\
itself. This energy corresponds to a thermal temperature of $T
\gtrsim$ 4$\times10^{5}$, implying a heating energy source of (soft)
X-ray photons ($k_{B}$ = 8.617$\times 10^{-5}$ eV /K).  \ciii is the
1$s2$2$s$2$p$ $^{3}$P$^{\circ}$ to 1$s^{2}$2$s^{2}$ $^{1}$S transition
(with $J=1\rightarrow0$) resulting in an energy of 52,390.75 cm$^{-1}$ and
a transition probability of $A_{ki} = 1.14\times10^{2}$ s$^{-1}$ \citep{Wiese1996}.

@@

  % \begin{tabular}{lll  cccc r }
  \begin{tabu}{l ll  ll cc c r }
    Object                               &   MJD      & line      & Line  Lumin.     &   FWHM                       &  $V_{\rm off}$         & E.W.                          & $\alpha_{\lambda}$  &   Catalogue \\                                   
    \rowfont{\color{blue}}       & 53498    & \civ      &  511$\pm$13    &   9593$\pm$287        &  1172$\pm$74      & 15.9$\pm$0.4      & $-1.64\pm0.01$       &  QSFit         \\    %% (NPR) 
    \rowfont{\color{blue}}       & 53498    & \civ      &  787                   &   5230$\pm$219        &  1118$\pm$133    & 30.1$\pm$1.21    & $-1.47\pm0.08$       &  Shen2011 \\
    \rowfont{\color{blue}}       & 53498    & \civ      &   403                  &   5119$^{(a)}$             &    ---                     &  ---                        &  ---                         &  DR12 SAS   \\
                                             & 53498     & \ciii      &  441$\pm$10   & 14959$\pm352^{(b)}$ &  2616$\pm$147    & 25.10$\pm$0.59    & $-1.65\pm0.01$      &  QSFit          \\  %% (NPR) 
                                             & 53498    & \ciii       &   144                 &   5119$^{(a)}$             &  ---                       &   ---                       &  ---                          &  DR12 SAS  \\
  \rowfont{\color{teal}}         & 53498     & \mgii     &  327$\pm$20   &   4907$\pm$387       &  $-274\pm419$     & 26.66$\pm$1.65    &   $-1.65\pm0.01$    &  $^{(d)}$QSFit  \\  %% (NPR) 
  \rowfont{\color{teal}}         & 53498     & \mgii     &  284                  &   4730$\pm$314       &  $-179\pm188$     & 32$\pm$3.88         &  $-1.87\pm0.06$     &  Shen2011 \\
 \multirow{2}{*}{{\bf J1205+3422}}  
                &     \textcolor{teal}{53948}     & \textcolor{teal}{\mgii}   & \textcolor{teal}{130} & \textcolor{teal}{5119$^{(a)}$}   &  \textcolor{teal}{---}   & \textcolor{teal}{---}        & \textcolor{teal}{---}    & \textcolor{teal}{DR12 SAS}    \\
                                 \cdashline{2-9}
                                            & 58538     & \lya      & 952$\pm$1.1    & 12242$\pm$15    &  $-1679\pm6$          &  165$\pm$0.2        &  ---                       &   QSFit  \\    %% (MJG)
   \rowfont{\color{blue}}       & 58538     & \civ      & 1037$\pm$5    & $>$15000             &  983$\pm$40            &  ---                        &  ---                       &   QSFit  \\   %% (NPR) 
                                            & 58538      & \ciii     &  167$\pm$0.9  & $>$15000            &  2734$\pm$46            &     45$\pm$0.2       &  ---                       &  QSFit  \\    %% (MJG)
    \rowfont{\color{teal}}      & 58538     & \mgii    &  216$\pm$1.4  & 13940$\pm$94    & $-465.2\pm38$         &  88$\pm$0.6	    &  ---                       &   QSFit  \\    %% (MJG)
                                          \cdashline{2-9}
                                           & 58693     & \lya     &  271$\pm$0.9    & 9637$\pm$52     &  $-447\pm13$          &  85.1$\pm$0.3          & ---                        &   QSFit  \\    %% (MJG)
    \rowfont{\color{blue}}    & 58693     & \civ      &   52$\pm$0.9    & 5046$\pm$26     &   1053$\pm$17         &   24.0$\pm$0.2          & ---                        &  QSFit \\     %% (MJG)
                                           & 58693     & \ciii     &   59$\pm$0.9    & 10751$\pm$        &  1097$\pm$77         &   36$\pm$0.6             & ---                        &  QSFit   \\    %% (MJG)
   \rowfont{\color{teal}}      & 58693     & \mgii    &  69$\pm$1.5    & 14983$\pm$346   &  $-190\pm134$       &    72$\pm$1.6           & ---                        &  QSFit   \\    %% (MJG)
                                                & 54553     & \lya      & 188                 &  3207                     &    ---                        &   ---                         & ---                    &   DR12 SAS  \\
   \rowfont{\color{blue}}          & 54553     & \civ      & 257$\pm$13   &  4550$\pm$371     &   55$\pm$450         &   31.8$\pm$1.5     &                                &  $^{(d)}$QSFit  \\   %% (NPR) 
   \rowfont{\color{blue}}          & 54553     & \civ      & 281                  &    4181$\pm$736   &    680$\pm$133       & 100.5$\pm$12  & $-0.14\pm0.68$        &  Shen2011   \\
   \rowfont{\color{blue}}          & 54553     & \civ      & 170                  &   4537$^{(a)}$        &    ---                       &   ---                         & ---                         &  DR12 SAS  \\    %% (NPR) 
                                                & 54553     & \ciii     &  130$\pm$10   &  3852$\pm$402    &  $-236\pm565$       &  36.7$\pm$2.8          &  $-1.47\pm0.20$    &  $^{(d)}$QSFit  \\
                                                & 54553     & \ciii     &  61                    &  4537$^{(a)}$          &  ---                         &  ---                           & ---                         &  DR12 SAS \\    %% (NPR) 
    \rowfont{\color{teal}}          & 54553      & \mgii  &  139                  &  4757$\pm$2224   &  $-944\pm568$        &   119$\pm$40          &  $-1.49\pm0.54$    &  Shen2011   \\
    \rowfont{\color{teal}}          & 54553      & \mgii  &  69                    &  4537$^{(a)}$           &    ---                        &  ---                          & ---                          &  DR12 SAS  \\   %% (NPR) 
                                                \cdashline{2-9}
                                                & 55832     & \lya     & 288$\pm$11    &  4444$\pm$243       &  -463$\pm$68         &  103.69$\pm$3.99   &                               &   QSFit  \\
                                                & 55832     & \lya     & 234                  &  4165.6$^{(a)}$         &    ---                       &   ---                         & ---                         &   DR12 SAS  \\    %% (NPR) 
\multirow{2}{*}{\bf {J1638+2827}}
 & \textcolor{blue}{55832} & \textcolor{blue}{\civ}    & \textcolor{blue}{63$\pm$3}  &   \textcolor{blue}{6052$\pm$250}  &  \textcolor{blue}{-117$\pm$103}  &  \textcolor{blue}{43.2$\pm$1.7}  &  \textcolor{blue}{-2.25$\pm$0.05} & QSFit    \\
    \rowfont{\color{blue}}           &  55832   &  \civ     &  ---               &    5210$\pm$226     &    ---                       &   42.8$\pm$2.0         & $-3.35$                 &     Ham17  \\
    \rowfont{\color{blue}}           &  55832   &  \civ     &  46                 &    5385$^{(a)}$           &    ---                       &   ---                         & ---                         & DR12 SAS \\
                                                 & 55832     & \ciii     & 15$\pm$5     &  11421$\pm$3654   &   $>$3000                &   14.8$\pm$4.5         &  $-2.25\pm0.05$   &        QSFit \\
                                                 &  55832    &  \ciii    &  11                 &     5385$^{(a)}$         &  ---                          &    ---                         &  ---                       &   DR12 SAS \\  
    \rowfont{\color{teal}}           &  55832     & \mgii   &  13                &     5385$^{(a)}$         &  ---                           &   ---                          &  ---                       &   DR12 SAS\\  
                                               \cdashline{2-9}
                                               & 58583       & \lya    &  785$\pm$1      & 4956$\pm$4    	&   $-641\pm2$            &   90$\pm$0.1   	  &  ---                          &  QSFit  \\ %% (MJG)
   \rowfont{\color{blue}}         & 58583      & \civ      &  311$\pm$1     & 5739$\pm$14	 &  $-167\pm6$             &   58$\pm$0.1          & ---                          &   QSFit  \\  %% (MJG)
                                               & 58583      & \ciii      &  52$\pm$0.8   &  3917.4	68.837      &  1514$\pm$127        &  124$\pm$2             & ---                          &   QSFit \\   %% (MJG)
   \rowfont{\color{teal}}           & 58583      & \mgii   &  157$\pm$2    &  10565$\pm$129    &  $-450\pm52$          &   92$\pm$1              & ---                          &   QSFit  \\  %% (MJG)
    \rowfont{\color{blue}}         &  56189     & \civ    &   32$\pm$3.5   &   7663$\pm$881       &    538$\pm$352       &   50.2$\pm$5.6      & ---                        &    QSFit  \\
    \rowfont{\color{blue}}         &  56189     & \civ    &   ---                 &   2994$\pm$620       &     ---                       &   42.2$\pm$5.6      & -1.59                      &    Ham17  \\
    \rowfont{\color{blue}}         &  56189     & \civ    &   19                  &    5218$^{(a)}$            &    ---                       &   ---                       &  ---                        &   DR12 SAS  \\
                                               &  56189      &  \ciii   &  34$\pm$6       &  13748$\pm$2869    &   1851$\pm$1140    &  63$\pm$12          &  $-0.46\pm0.21$    &   QSFit  \\
                                               &  56189      & \ciii    &  7                     &     5218$^{(a)}$          &  ---                         &     ---                     & ---                         &   DR12 SAS \\  
    \rowfont{\color{teal}}          & 56189      & \mgii  &  25$\pm$6       &   7253$\pm$1712     &   $-931\pm708$      &  51$\pm$10.95      &  $-0.46\pm0.21$   &   QSFit   \\
    \rowfont{\color{teal}}         &  56189      &  \mgii &  13                   &     5218$^{(a)}$          &  ---                         &   ---                        &  ---                       &   DR12 SAS \\  
                                                  \cdashline{2-9}
                                              & 56960         & \lya    & 121$\pm$38     & 3580$\pm$673       &     -16$\pm$171     &  13.52 $\pm$4.21    & ---                        &   QSFit   \\  
\multirow{2}{*}{{\bf J2228+2201}}
           & \textcolor{blue}{56960} & \textcolor{blue}{\civ}  & \textcolor{blue}{229$\pm$4}      &  \textcolor{blue}{8911$\pm$169}   &   \textcolor{blue}{92$\pm$68}  &   \textcolor{blue}{46.8$\pm$0.9}    & ---    & \textcolor{blue}{QSFit}     \\   
                                               & 56960    & \ciii      & 185$\pm$5        &        -                      &  2701$\pm$225      &   47.75$\pm$1.29     & ---                      &   QSFit    \\  
   \rowfont{\color{teal}}           & 56960    & \mgii   &   99$\pm$4        &  7312.6$\pm$340   &   188$\pm$137      &   50.75$\pm$2.21     & ---                      &   QSFit   \\
                                               \cdashline{2-9}
                                               & 58693     & \lya      &  447$\pm$5       & 8133$\pm$93       &   613$\pm$130       &        56$\pm$0.6     &  ---                    	 &   QSFit  \\%% (MJG)
     \rowfont{\color{blue}}        & 58693     & \civ      &  41$\pm$1        &  4914$\pm>$65    &   160$\pm$27         &   25$\pm$0.3          & ---                         & QSFit   \\  %% (MJG)
                                               & 58693     & \ciii      & 107$\pm$1.2    &  $>$15000             &  2422$\pm$67        &   ---                       & ---                          &  QSFit    \\  %% (MJG)
     \rowfont{\color{teal}}        & 58693     & \mgii    & 177$\pm$1.1    &  $>$15000             &  1000$\pm$2617    &   16$\pm$36         & ---                           &   QSFit  \\  %% (NPR) 
     %    \end{tabular}
    \end{tabu}
    \caption{Line Measurement information for the nine epochs for the 3 quasars.
      Line Luminosity is in units of 10$^{42}$ erg s$^{-1}$; FWHM and $V_{\rm off}$ in km s$^{-1}$,
      where positive values of $V_{\rm off}$ means the line is blueshifted.
      Equivalent widths are \AA\.  
      Ham17 is \citet{Hamann2017}.
      DR12 SAS is the line measurement information from the SDSS DR12 
      Science Archive Server (SAS).
          $^{(a)}$Emission lines of a common ``width group'', in this case,
    \civ1549, \heii1640, \ciii1909 and \mgii2800 are constrained to have
    the same intrinsic velocity width in the SDSS spectral line fitting
    procedure \citep{Bolton2012}. 
      %$^{(a)}$ $\text{FWHM}=2\sqrt{2\sigma^2\ln 2}=\sigma\sqrt{8\ln 2}$.
      Positive values of Voff means the line is blueshifted.
%      $^{(b)}$Bit 3: FWHM value hits a limit in the fit
      Notes: QSFit does not fit the \mgii line for J1638+2827 MJD
      54553 or 55832. QSFit does not fit the \civ line for J2228+2201 MJD 56189.
      $^{(d)}$Emission line modelled with two components.
      The different colours of text are merely for readability.
 \label{tab:LineMeasurements}

>>>>

  \begin{centering}
    \begin{tabular}{l r  r r   lll lll  r r}
      Line                 & $\lambda$ &  Transition  & Ionization  &  \multicolumn{6}{c}{Transition Levels}                                                                                           & Wavenumber   & $A_{i,j}$                    \\
%                              &    / \AA\    &      / eV             &  / eV            &   Lower                  & Conf.      &  $J$       & Upper                      &  Conf.                       & $J$       & / cm$^{-1}$    &  / s$^{-1}$                \\      \hline
                              &  / \AA\     &  energy  / eV &  energy  / eV   &    \multicolumn{3}{l}{Lower}    &  \multicolumn{3}{l}{Upper}                                                         & / cm$^{-1}$    &  / s$^{-1}$                \\      \hline
      H LyLim           &   912.324   & 13.5984           & 13.5984      & 1$s$                      & $^2$S     & 1/2        & $\infty$                  &                                 &             & 109 678.7       & 1.23$\times10^{2}$  \\
      H Ly$\alpha$  &  1215.670  & 10.1988          & 13.5984      & 1$s$                       & $^2$S      & 1/2        & 2                             &                                 &             &  82 259.2       &  4.67$\times10^{8}$  \\
      \nv                  &  1238.821  & 10.0082          &  97.8901     &  1$s^{2}$2$s$        &  $^{2}$S   &  1/2       & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &   3/2    &  80 721.9        & 3.40$\times10^{8}$   \\
      \nv                  &  1242.804  &  9.9762            &  97.8901     &  1$s^{2}$2$s$       &  $^{2}$S   &  1/2       &  1$s^{2}$2$p$         &  $^{2}$P$^{{\rm o}}$ &  1/2     &  80 463.2        & 3.37$\times10^{8}$  \\
      \civ                 &  1548.187  &  8.0083            &  64.4935     &  1$s^{2}$2$s$       &   $^{2}$S  & 1/2        & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &  3/2     &  64 591.7        & 2.65$\times10^{8}$  \\
      \civ                 &  1550.772  &  7.9950          &  64.4935     & 1$s^{2}$2$s$          &  $^{2}$S   & 1/2        & 1$s^{2}$2$p$          &  $^{2}$P$^{{\rm o}}$ &  1/2     &   64 484.0       & 2.64$\times10^{8}$  \\
      \ciii                 &  1906.683  &  6.5026    & 47.8878      & 1$s^{2}$2$s^{2}$         &   $^{1}$S   & 0            & 1$s^{2}$2$s$2$p$  &  $^{3}$P$^{{\rm o}}$ &   2        &   52 447.1       & 5.19$\times10^{-3}$ \\
      \ciii                 &  1908.734  &  6.4956    & 47.8878      & 1$s^{2}$2$s^{2}$         &  $^{1}$S    & 0            & 1$s^{2}$2$s$2$p$  &  $^{3}$P$^{{\rm o}}$ &  1         &  52 390.8        & 1.14$\times10^{2}$  \\
       \mgii              &  2795.528  &  4.4338    & 15.0353       & 2$p^{6}$3$s$             &  $^{2}$S    & 1/2        & 2$p^{6}$3$p$          &  $^{2}$P$^{{\rm o}}$ &   3/2     &  35 760.9       & 2.60$\times10^{8}$  \\
      \mgii               &  2802.705  &  4.4224    & 15.0353        & 2$p^{6}$3$s$            &  $^{2}$S    & 1/2        & 2$p^{6}$3$p$          &  $^{2}$P$^{{\rm o}}$ &   1/2     &  35 669.3       & 2.57 $\times10^{8}$ \\
      H Ba $\beta$   &  4861.333  &  2.5497    & 13.5984       & 2                                 &                 &               & 4                             &                                 &              &  20 564.8       & 8.42$\times10^{6}$  \\
    \caption{Strong UV/optical spectral emission lines in quasars, and their atomic data.
      Data from the NIST Atomic Spectra Database       \citep{Kramida2018, Kramida2019}.
      The Transition Energies are $E=hc/\lambda$ for the given wavelength. The Ionization Energy is the
      energy required to ionize the given species, e.g. 64.49 eV are needed to create a \cv\ ion.
      Transitions Level configurations are given in standard spectroscopic notation
      %($N^{2s+1}$ $L_{j}$. 
      $A_{i,j}$ are transition probabilities.
%      $A_{i,j}$ are \href{https://www.nist.gov/pml/atomic-spectroscopy-compendium-basic-ideas-notation-data-and-formulas/atomic-spectroscopy-6}{transition probabilities}.} 
%      such that the radiative lifetime $\tau_{k}$ of an atomic level $k$ is related to the sum of transition probabilities to all levels $i$ lower in energy than $k$
%      The 1548.202 and 1550.774 \AA\ emission doublet is created by the 2$p$ $^{2}P_{0}$ $-$ 2$s$ $^{2}S$ transition, split by total angular momentum $J= 3/2$ and $1/2$. 
      Data from the NIST Atomic Spectra Database       \citep{Kramida2018, Kramida2019}.}
    %%  Mg II Z = 12, Na isoelectronic sequence  
  \label{tab:atomic_lines}
  \end{centering}

@@

Details of the atomic transitions that produce strong rest-frame
UV/optical lines in quasars are given in Table~\ref{tab:atomic_lines}.
In this paper we use the wavelengths of 1548.202 and 1550.774~\AA\ for
the \civ\ doublet \citep{Kramida2018}.
%% The ground state of carbon is 1$s^2$ 2$s^2$ 2$p^2$. \
%% Using the \href{https://physics.nist.gov/PhysRefData/ASD/ionEnergy.html}{NIST Atomic Spectra Database Ionization Energies Form}
For ionisation energies, 11.3 eV is the energy required for C~I to dislodge
one electron and become singly-ionised C~II; 24.4 eV is then the
(`additional') energy needed for singly-ionised C~II to dislodge an
additional electron, and become doubly-ionised C~III, and 47.89 eV
(3.519 Ry) is required for doubly-ionised C~III become triply-ionised
\civ.  64.49 eV (4.74 Ry) is the energy needed to ionize \civ\
itself. This energy corresponds to a thermal temperature of $T
\gtrsim$ 4$\times10^{5}$, implying a heating energy source of (soft)
X-ray photons ($k_{B}$ = 8.617$\times 10^{-5}$ eV /K).

@@

\begin{table*}
  \centering
  \input{emission_line_comparison_tab}

  \caption{Line Measurement information for the nine epochs for the 3 quasars.
    Line Luminosity is in units of 10$^{42}$ erg s$^{-1}$; FWHM and $V_{\rm off}$ in km s$^{-1}$,
    where positive values of $V_{\rm off}$ means the line is blueshifted.
    Equivalent widths are \AA\.  
    Shen11 is \citet{Shen2011}. 
    Ham17 is \citet{Hamann2017}.
    DR12 SAS is the line measurement information from the SDSS DR12 
    Science Archive Server (SAS).
    $^{(a)}$Emission lines of a common ``width group'', in this case,
    \civ1549, \heii1640, \ciii1909 and \mgii2800 are constrained to have
    the same intrinsic velocity width in the SDSS spectral line fitting
    procedure \citep{Bolton2012}. 
    % $^{(a)}$ $\text{FWHM}=2\sqrt{2\sigma^2\ln 2}=\sigma\sqrt{8\ln 2}$.
    Positive values of Voff means the line is blueshifted.
    % $^{(b)}$Bit 3: FWHM value hits a limit in the fit
    Notes: QSFit does not fit the \mgii line for J1638+2827 MJD
    54553 or 55832. QSFit does not fit the \civ line for J2228+2201 MJD 56189.
    $^{(d)}$Emission line modelled with two components.
    The different colours of text are merely for readability.
    }
 \label{tab:LineMeasurements}
\end{table*}
